Manuscript 1 code

### 2024-10-11 manuscript_1_code.Rmd
comment out ggsave

filtered_even_stab_effects_site <- even_stab_emm_site %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(evenness_mean >= min_evenness & evenness_mean <= max_evenness)
# This is useless
(even_stab_plot_site <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = evenness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_even_stab_effects_site, aes(x = evenness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_even_stab_effects_site, aes(x = evenness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "Evenness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
ggsave(filename = "output/evenness_stability_site.png", even_stab_plot_site, height = 10, width = 14)
```

>>>>

filtered_even_stab_effects_site <- even_stab_emm_site %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(evenness_mean >= min_evenness & evenness_mean <= max_evenness)
# This is useless
(even_stab_plot_site <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = evenness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_even_stab_effects_site, aes(x = evenness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_even_stab_effects_site, aes(x = evenness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "Evenness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# ggsave(filename = "output/evenness_stability_site.png", even_stab_plot_site, height = 10, width = 14)
```
